---
title: "Data Cleaning Challenge"
output: html_document
author: 'Paul Bloom'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Part 1: Conditionals & logic

Below is a numeric vector `num_vec` and a vector of strings `string_vec` . See if you can figure out how to do the following

  * A: select all items in `num_vec` above 50
  * B: select all odd numbers in `num_vec`
  * C: select items 2 through 4 in `string_vec`
  * D: select items in `string_vec` starting with the letter g
  * E: select items in `string_vec` that contain the letter a
  * F: select the items in `num_vec` matching the items in `string_vec` containing the letter g
  * G: select the items in `string_vec` matching the items in num vec that are even

```{r}
num_vec = c(1:3, 101:103)
string_vec = c('grape', 'banana', 'fruit', 'banana2', 'grape fruit', 'grapefruit')
num_vec
string_vec
```


# Part 2: Indexing dataframe with the tidyverse


Make sure this bit works -- if it crashes you'll need to make sure to install the tidyverse correctly with `install.packages('tidyverse')`

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```


## This part is setting up the dataframe

```{r}
df = data.frame(nums = num_vec, 
                strings = string_vec,
                random1 = rnorm(n = length(num_vec)),
                random2 = rnorm(n = length(num_vec)))

head(df)
```


See if you can do the following with the dataframe `df`. For each one, print out the dataframe so you can make sure you've gotten it the way you want!

  * A: Print out all items in the column `strings` containing the string 'grape'
  * B: Make a dataframe called 'grape_df' that has only rows of the data where the string 'grape' is in strings (as in part A)
  * C: Make a dataframe called 'random_df' that has only the columns containing the word 'random' 
  * D: Make a datframe called 'positive_grape', containing the columns 'strings' and 'random1', and only rows where random1 is positive

