---
title: "data_cleaning"
author: "Paul Bloom"
date: "11/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load in survey data


```{r}
library(tidyverse)
df = read_csv('../data/kaggle_young_people_survey/responses.csv')
```


# Numeric indexing of dataframes

Reference data in the dataframes using [] and numbers


```{r}
# give first value in column Music
df$Music[1]
df$`Responding to a serious letter`[4:20]


# give first value in first column
# [row, column]
df[3:4,1:4]

# replace a value in the dataframe
df[1,4] = 3
df[1,4]
```

# using the tidyverse for data cleaning

Getting certain rows: `dplyr::filter`
  Exclude certain pieces of data
  Analyze/plot subsets of data
  
Getting certain columns: `dplyr::select`
  Reducing data size
  Focusing on things you want to work with


Why tidyverse is so useful? We can access columns without `$`

SQL -- this is where a lot of the tidy commands are coming from 
  "relational databases"

## using `dplyr::select` to get certain columns
```{r}
df_cleaned = df %>% 
  dplyr::select(-c(Folk, Punk, Dance)) %>%
  dplyr::select(contains('p', ignore.case = FALSE))
  
df %>%
  dplyr::select(starts_with('spending'))

df_end = df %>%
  dplyr::select(ends_with('s') & contains('p'))
```

## using `dplyr::filter` to get certain rows

how does filter work?

```{r}
country1 = df_cleaned %>% dplyr::filter(Country == 1 | Musical == Rock)

sum(is.na(df_cleaned$Country))

# base R way of doing it
country2 = df_cleaned[df_cleaned$Country == 1, ]

df_cleaned$Country == 1

sum(is.na(country1$Country))
sum(is.na(country2$Country))
```

# Multistep piping

```{r}
df2 = df %>% 
  dplyr::select(-c(Folk, Punk, Dance)) %>%
  dplyr::select(contains('c', ignore.case = TRUE)) %>%
  dplyr::filter(Country == 1 & Musical == Rock & Alcohol != 'drink a lot')
```