---
title: "functions"
author: "Paul Bloom"
date: "10/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

# "runs all code in the script"
source('function_script.R')
df = read_csv('../data/familiar_music_database.csv')
```


# What is a function / why is a function useful?

* Give output from inputs
* They manipulate data
* They can be "called" (run) to do specific actions
* They can be flexible -- to do different actions / take in different data, give diffrent output

What can we use them for?

* We can write a lot less code (your code is cleaner)
* Helps cut down on errors
* Increases communication potential of code -- you can share it in a way that isn't too complex

"If you have to do something more than once, write a function to do it"


# Anatomy of a function
```{r}
# CREATING the function

# outside


# RUN the function
greet(person_name = 'Sarah')
greet(person_name = 'Anshita')

```

# Best practice: use "return"

```{r}

my_sum = custom_addition(2, 25)

my_sum + 29

my_sum + 1



bing_crosby = search_artist(artist_name = "bing crOSby", data_frame = df)
```


Print: just display to the console
Return: send data out of the function (these data can be used further)